\large Autonomous Aerial Exploration for Topological Mapping of Mars Environments

### 2019-01-10 Dissertation/Defense/scitech19_presentation.tex
minor fixes to the e mars presentation... looking good after single readthrough

\begin{frame}
\frametitle{Research Contributions}
\begin{itemize}
	\item Occupancy Grid Mapping
		\begin{itemize}
		\item Computation of the exact occupancy probability of the initially-uncertain Mars environment
		\item Incorporation of prior knowledge and new measurements
		\item Bayesian information fusion in 3D
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Novel approach to predicting future map uncertainty
		\item Optimal planning to maximize information gain
		\item Complicated 3D Mars environment explicitly considered in pose selection and path planning
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{itemize}
	\item Apply Dijkstra's algorithm about 3D graph of occupancy grid
	\item Locations and associated distance costs for reachable positions in 3D
\end{itemize}
\begin{figure}
	\centering
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{mars_closeup.png}
        		\caption{Mars Simulation Poses}
    	\end{subfigure}
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{disconnected_costmap.png}
        		\caption{3D Dijkstra's Search}
    	\end{subfigure}
\label{fig:marsZoomedIn}
\end{figure}
\end{frame}

\begin{frame}
	\frametitle{3D Mars Exploration Conclusions}
	\begin{itemize}
		\item Expected information gain of several poses in 3D space capturing complex obstacles
		\item Distance cost accounts for collision-avoidance
		\item Mapping and exploration are computationally-efficient for real-time implementation
	\end{itemize}
		\begin{figure}
		\centerline{
			\includegraphics[width=0.8\columnwidth]{node_diagram_3D_mars.png}
		}
		\label{fig:NodesDiagram}
	\end{figure}
\end{frame}

>>>>

\begin{frame}
\frametitle{Research Contributions}
\begin{itemize}
	\item Occupancy Grid Mapping
		\begin{itemize}
		\item Computation of the exact occupancy probability of the initially-uncertain Mars environment
		\item Incorporation of prior knowledge and new measurements
		\item Bayesian information fusion in 3D
	\end{itemize}
	\pause
	\item Autonomous Exploration
	\begin{itemize}
		\item Novel approach to predicting future map uncertainty
		\item Optimal planning to maximize information gain for a \emph{flying} Mars robot
		\item Complicated 3D Mars environment explicitly considered in pose selection and path planning
	\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{itemize}
	\item Apply Dijkstra's algorithm about 3D graph of occupancy grid
	\item Locations and associated distance costs for reachable positions in 3D
\end{itemize}
\begin{figure}
	\centering
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{mars_closeup.png}
        		\caption{Mars Simulation Poses}
    	\end{subfigure}
	\begin{subfigure}[t]{0.45\columnwidth}
           	\centering
          	\includegraphics[height=0.5\textwidth]{connected_costmap.png}
        		\caption{3D Dijkstra's Search}
    	\end{subfigure}
\label{fig:marsZoomedIn}
\end{figure}
\end{frame}

\begin{frame}
	\frametitle{3D Mars Exploration Conclusions}
	\begin{itemize}
		\item Expected information gain of several poses in 3D space capturing complex obstacles while flying
		\item Distance cost accounts for collision-avoidance
		\item Mapping and exploration are computationally-efficient for real-time implementation
	\end{itemize}
		\begin{figure}
		\centerline{
			\includegraphics[width=0.8\columnwidth]{node_diagram_3D_mars.png}
		}
		\label{fig:NodesDiagram}
	\end{figure}
\end{frame}
